### 2021-09-03 revision/laySum.tex
added phd thesis.

Predicting the movement of gravel through river channels is important to manage environmental issues involving rivers, since moving gravel can destabilize river channels.
A majority of models assume gravel flows as if it were a heavy fluid, but this description is crude considering how gravel actually moves.
In this thesis, I instead describe gravel movement as the result of individual grains bouncing and rolling along the streambed.
Using this concept, I calculate the downstream flow rate of gravel, study how this flow rate depends on the shape of the bed, and predict how quickly individual grains move downstream.
This research produces a more realistic description of how gravel moves in river channels which helps us understand how rivers change through time.

>>>>

Predicting the flow rates of gravel through river channels is important to manage environmental issues involving rivers.
Most approaches to predict gravel flow consider gravel as if it were a heavy fluid.
This description oversimplifies the problem, since gravel flow is actually individual grains bouncing and rolling downstream, which is hardly like a fluid.

In this thesis, I consider gravel flow as the result of individual grains. Using physics and probability, I calculate how fast individual grains move downstream, then I demonstrate how to use their downstream movement paths to predict overall gravel flow rates.
This research produces a more realistic description of gravel movement in rivers which helps us understand how rivers change through time.
